---
title: "countFusionsTumor_and_plot.Rmd"
author: Lincoln
date: 9.13.18
output: html_document

---

```{r}
setwd("/home/rstudio/01-STARfusion_R_manipulation/01-tumorCellsOut/")
```

get cells list
```{r}
t_cells <- list.files(path = ".", pattern = ".tsv")
```

raw counts
```{r}
raw_countsT <- c()

for(t_cell in t_cells){
  df_t <- read.csv(t_cell, sep = "\t", header = T)
  raw_countT <- nrow(df_t)
  raw_countsT <- c(raw_countsT, raw_countT)
}
```

```{r}
ave(raw_countsT)[1]
```

what about total fusion reads? 
```{r}
read_countsT <- c()

for(t_cell in t_cells){
  df_t <- read.csv(t_cell, sep = "\t", header = T)
  read_countT <- sum(df_t$JunctionReadCount) + sum(df_t$SpanningFragCount)
  read_countsT <- c(read_countsT, read_countT)
}
```

```{r}
ave(read_countsT)[1]
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

WANT TO PLOT SOME OF THESE DATA

get cell names
```{r}
t_cellNames <- c()

for(i in 1:length(t_cells)){
  currCell <- ""
  currList <- strsplit(t_cells[i], "_")
  currCell <- paste(currList[[1]][1], currList[[1]][2], sep = "_")
  t_cellNames <- c(t_cellNames, currCell)
}
```

turn this thing into a dataframe, so that we can plot it
```{r}
read_countsT <- as.data.frame(read_countsT)
#row.names(read_countsT) <- t_cellNames
colnames(read_countsT) <- "counts"
```

how to plot? 
```{r}
ggplot(read_countsT, aes(x = counts)) + geom_density() # horrible
ggplot(read_countsT, aes(x = "counts", y = counts)) + geom_point() # hmmm

basicBox <- ggplot(read_countsT, aes(x = "counts", y = counts)) + geom_boxplot(width = 0.25) # horrible
basicBox
basicBox + scale_y_continuous(trans = 'log2') # a little better...
advBox <- basicBox + scale_y_continuous(trans = 'log2') + ylim(0, 3000)
advBox

# can i get a violin in there? 
advBox + geom_violin()
```

more plotting
```{r}
p <- ggplot(read_countsT, aes(x = "counts", y = counts))
p + geom_boxplot(width = 0.25) + scale_y_continuous(trans = 'log2')
p + geom_boxplot(width = 0.25) + scale_y_continuous(trans = 'log2') + ylim(0, 3000)
p + geom_violin() + geom_boxplot(width = 0.25, fill = 'black', outlier.color = NA) + scale_y_continuous(trans = 'log2') + ylim(0, 3000) + stat_summary(fun.y=median, geom="point", fill="white", shape=21, size=2.5)
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

BOTH ON SAME PLOT?

append both to same df
```{r}
readCounts_df <- read_countsT
colnames(readCounts_df) <- "tumorCounts"
readCounts_df$healthyCounts <- NA
readCounts_df$healthyCounts[1:409] <- read_countsH$counts
readCounts_df$healthyCounts[410: 454] <- NA
#row.names(readCounts_df) <- NA
```

need to reshape? 
```{r}
library(reshape2)

meltData <- melt(readCounts_df)
meltData <- meltData[1:863, ] # get rid of the NAs
boxplot(data= meltData, value~variable) # works!!
```

plot
```{r}
p <- ggplot(meltData, aes(factor(variable), value))
p + geom_boxplot() # works!!

p + geom_boxplot(width = 0.25, fill = 'black', outlier.color = NA) + stat_summary(fun.y=median, geom="point", fill="white", shape=21, size=2.5)

pdf("fusion_read_counts_boxplot.pdf", 10, 10)
p + geom_boxplot(width = 0.25, fill = 'black', outlier.color = NA) + scale_y_continuous(trans = 'log2') + stat_summary(fun.y=median, geom="point", fill="white", shape=21, size=2.5)
dev.off()

p + geom_boxplot(width = 0.25, fill = 'black', outlier.color = NA) + scale_y_continuous(trans = 'log2') + ylim(0, 3000) + stat_summary(fun.y=median, geom="point", fill="white", shape=21, size=2.5)
```

hmmm...ok looks like the read count values are almost the same...
```{r}
hc_indices <- which(meltData$variable == "healthyCounts")
ave(meltData$value[hc_indices])[1]

tc_indices <- which(meltData$variable == "tumorCounts")
ave(meltData$value[tc_indices])[1]
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

SAME THING, BUT FOR RAW FUSION COUNTS

append both to same df
```{r}
rawCounts_df <- as.data.frame(raw_countsT)
colnames(rawCounts_df) <- "tumorCounts"
rawCounts_df$healthyCounts <- NA
rawCounts_df$healthyCounts[1:409] <- raw_countsH
rawCounts_df$healthyCounts[410: 454] <- NA
```

need to reshape? 
```{r}
library(reshape2)

meltData_raw <- melt(rawCounts_df)
meltData_raw <- meltData_raw[1:863, ] # get rid of the NAs
boxplot(data= meltData_raw, value~variable) # works!!
```

plot
```{r}
p1 <- ggplot(meltData_raw, aes(factor(variable), value))
p1 + geom_boxplot() # works!!

p1 + geom_boxplot(width = 0.25, fill = 'black', outlier.color = NA) + stat_summary(fun.y=median, geom="point", fill="white", shape=21, size=2.5)

pdf("fusion_raw_counts_boxplot.pdf", 10, 10)
p1 + geom_boxplot(width = 0.25, fill = 'black', outlier.color = NA) + scale_y_continuous(trans = 'log2') + stat_summary(fun.y=median, geom="point", fill="white", shape=21, size=2.5)
dev.off()

p1 + geom_boxplot(width = 0.25, fill = 'black', outlier.color = NA) + scale_y_continuous(trans = 'log2') + ylim(0, 3000) + stat_summary(fun.y=median, geom="point", fill="white", shape=21, size=2.5)
```

